---
title: "ames-map"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(AmesHousing)
library(leaflet)

theme_set(theme_light())
```

## Purpose

Make a map of the Ames, Iowa housing dataset to show what could be useful with the leaflet package.

## Planning

I want to have three pages:

1. House explorer - map with the leaflet package. Each house is on the map with an HTML popup that shows features about the house. Can have a slider to select years.

2. Data explorer - A page with a tabset panel, showing categorical and continuous variables relationship with house price on the y axis in the case of continuous. For continuous - I want to have 

Maybe a third tabset panel with the relationship between continuous variables.

3. An explanation of the most important variables that determine house price. First a simple penalized logistic regression model. Then an xgboost model with the performance metrics as well as the variable importance plots.

## Process

I kinda have to do the modelling first so that I can see what is important to put in the leaflet plot? No, perhaps I do it the other way around - with the map first and then come back with the important variable.

## Reading in data.

```{r}
df <- AmesHousing::ames_raw %>% 
    janitor::clean_names()

df_geo = AmesHousing::ames_geo %>% 
    janitor::clean_names()

df = df %>% 
    inner_join(df_geo)
```

## EDA

```{r}
library(skimr)

df %>% 
  skim()
```

Map in ggplot. Showing price.

```{r}
df %>% 
    ggplot(aes(x = longitude, y = latitude, colour = sale_price)) +
    geom_point() +
    scale_color_gradient2(low = "blue", high = "red", mid = 4e5,
                          labels = scales::dollar_format())
```

Relationship between year built and price. We can see that newer buidlings sell for more.

```{r}
df %>% 
  ggplot(aes(year_built, sale_price)) +
  geom_point() +
  geom_smooth() +
  scale_y_log10(labels = scales::dollar_format()) +
  labs(x = "Year built",
       y = "Sale price")
```

What types of houses are built at different times?

```{r}
df %>% 
  ggplot(aes(year_built, fill = bldg_type)) +
  geom_density() +
  facet_wrap(~ bldg_type, nrow = 5) +
  theme(legend.position = "none")
```


```{r}
df %>%
  mutate(
    transformed_price = log2(sale_price),
    price_color = colorNumeric(c("blue", "red"), sale_price)(sale_price)
  ) %>%
  gather(
    key, value,
    pid,
    sale_price,
    year_built,
    neighborhood,
    lot_area,
    overall_cond,
    overall_qual
  ) %>%
  mutate(
    key = str_to_title(str_replace_all(key, "_", " ")),
    key = paste0("<b>", key, "</b>")
  ) %>%
  replace_na(list(value = "Unknown")) %>%
  nest(data = c(key, value)) %>%
  mutate(html = map(data,
    knitr::kable,
    format = "html",
    escape = FALSE,
    col.names = c("", "")
  )) %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(
    lat = ~latitude,
    lng = ~longitude,
    color = ~price_color,
    popup = ~html,
    radius = 2
  ) %>%
  addMeasure()
```

### Descriptives

```{r}
df %>% count(utilities, sort = T)
df %>% count(ms_zoning, sort = T)
df %>% count(overall_qual, sort = T)
df %>% count(overall_cond, sort = T)
df %>% count(house_style, sort = T)
df %>% count(roof_style, sort = T)



df %>% skimr::skim()
```

### Desc stats

```{r}
df %>%
  ggplot(aes(overall_qual,
    overall_cond,
    fill = sale_price
  )) +
  geom_tile() +
  scale_fill_gradient2(
    low = "blue", high = "red", mid = 4e5,
    labels = scales::dollar_format()
  )
```


### Shiny components
```{r}

df %>% 
  select(where(is.numeric)) %>%
  gather(key, value, -sale_price) %>% 
  filter(key == "garage_area") %>% 
  ggplot(aes(value, sale_price)) +
  geom_point(alpha = .5, colour = "midnightblue") +
  geom_smooth() +
  scale_x_log10(labels = number_format()) +
  scale_y_log10(labels = dollar_format()) +
  labs(x = glue("lot_area"),
       y = "Sale price")
```


```{r}
# normally dist vars
df %>% 
  select(lot_frontage,
         lot_area,
         year_built,
         year_remod_add,
         gr_liv_area)

# density plot ones.
df %>% 
  select(overall_qual,
         overall_cond,
         bsmt_full_bath,
         full_bath,
         half_bath,
         bedroom_abv_gr,
         kitchen_abv_gr,
         tot_rms_abv_grd,
         fireplaces,
         garage_cars)
```


```{r}
df %>% 
  select(where(is.character)) %>% 
  skimr::skim()

df %>% 
  count(lot_shape)

# character ones to show as density plots
# need to have an if else that has is.numeric => no reordering but if is.character, then reorder them.
df %>% 
  select(ms_zoning,
         lot_shape)
```


```{r}
df %>% 
  select(where(is.numeric)) %>% 
  gather(key, value, -sale_price) %>% 
  filter(key == "lot_area") %>% 
  ggplot(aes(value, sale_price)) +
  geom_point(alpha = .5, colour = "midnightblue") +
  geom_smooth() +
  scale_x_log10(labels = number_format()) +
  scale_y_log10(labels = dollar_format()) +
  labs(x = glue("lot_area"),
       y = "Sale price")
```

```{r}
library(ggridges)

df %>%
  ggplot(aes(sale_price, y = factor(garage_cars), fill = factor(garage_cars))) +
  geom_density_ridges() +
  scale_x_log10(labels = dollar_format()) +
  theme(legend.position = "none") +
  labs(
    x = "Sale price",
    y = glue("Overall condition")
  )
```

### Modelling

```{r}
library(tidymodels)
spl <- initial_split(df, strata = sale_price)

df_train <- 
```

